\vspace{.5cm } \LARGE{If you see something, say something (to others):} \\ \large{The effects of socially-contingent corrections on spreads of misinformation on social networks}

### 2018-02-06 main.tex
Update on Overleaf.

\addbibresource{}

@@

Research on political misinformation and motivated reasoning generally suggests that fact-checking (or corrections) on false information has only limited effects due to inherent tendency of humans to directionally process the (politically) relevant information. However, a small line of research suggests that the effect of political fact-checking on social network may be socially contingent.

>>>>

\addbibresource{abm_misinformation_lit.bib}

@@

There has been an explosive interest among public and academics alike on how people directionally process and maintain factually false (or at least factually dubious) information (\cite{LEWANDOWSKY_JARMC2017}), and further, how corrections to such false information is received under various scenarios (\cites{LEWANDOWSKY_JARMC2017}; \cites{thorson_2016}). Research on political misinformation and motivated reasoning generally suggests that fact-checking (or corrections) on false information has only limited effects due to inherent tendency of humans to directionally process the (politically) relevant information. However, a small line of research suggests that the effect of political fact-checking on social network may be socially contingent.
